---
title: "artists-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{artists-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(artists)
```

# Artists package

## Introduction

This vignette describes the use of the functions of the package "artists". We have five functions:

- Topsongslyrics
- TopAlbum
- Compare.year
- Compare.lyrics
- Geniusdashboard

In this vignette we explain you the use of those functions with some examples.

## Topsongslyrics

This function returns the top 10 songs of the artists you like with their lyrics. You also have the possibility to print a term frequency graph, a worlcloud and return directly in the environment the following variables: df, token, corpus, dtm, freq and covariance matrix.

Example of use for the artist Lady Gaga:

```{r}
# Topsongslyrics(
#   name = "Lady Gaga",
#   tfgraph = TRUE,
#   wordcloud = TRUE,
#   lang = "en",
#   environment.return = TRUE,
#   local = TRUE
# )
```

## TopAlbum

This functions returns the name and the released year of the albums of the artists you like.

Example of use for the artist Lana Del Rey:

```{r}
# TopAlbums("Lana Del Rey", local = TRUE)
```

## Compare.year

This functions returns a density plot of the year of activity & popularity of two artists you like.

Example of use with the artists Lady Gaga and Lana Del Rey:

```{r}
# compare.year("lady gaga", "lana del rey", local = TRUE)
```

## Compare.lyrics

This function returns a plot that compares the lyrics between two artists you like.

Example of use with the artists Lady Gaga and Lana Del Rey:

```{r}
# compare.lyrics("lady gaga", "lana del rey")
```

## Geniusdashboard

This functions launches a shiny app dashboard with the following interactions:

- By choosing one artist of your choice the dashboard displays a term frequency plot, an average sentiment plot, a sentiments by song plot and a sentiments globally plot.
- By choosing two artists of your choice the dashboard displays between the two artists a comparison of a popular albums distribution, an LDA analysis with a theta plot and a phi plot, and a keyness plot.

Example of use:

```{r}
# Geniusdashboard(artists.df, lang.df)
```

